### 2020-03-06 ChapterProblemDefinition/chapterProblemDefinition.tex
Updated: Summary for Problem Definition

In this chapter the requirements of a solution to scalable real-time physics and the challenges of distributing a real-time physics engine will be discussed, using a naive approach as an example. Some potential solutions to distributing real-time physics and their trade-offs will be considered. Finally, our proposed solution (AP) will be described, along with high-level overviews of the challenges with this approach and our implemented and proposed solutions.

@@

@@

1. An object may be overlapping two auras from different servers. Given appropriate velocity, this could result in object migration, followed by aura collision, followed by migration and then repeating the process again. For example, Objects K, L and M in Fig. \ref{AuraProj}. Object K lies inside the auras of both Object L and M.

@@

2. Two objects on different servers may both trigger the migration of the other. For example, Objects C and D in Fig. \ref{AuraProj}. Suppose the two objects are moving towards each other. Object C collides with the aura of object D and begins migrating to Server 1. Before Object C is received (and the message processed), object D collides with the aura of Object C and begins migrating to Server 0. The two objects remain on different servers and the process can repeat again, indefinitely.

@@

>>>>

In this chapter the requirements of a solution to scalable real-time physics and the challenges of distributing a real-time physics engine will be discussed, using a naive approach as an example. Some potential solutions to distributing real-time physics and their trade-offs will be considered. Finally, this study's proposed solution, AP, (originally presented in \cite{brown2019aura}) will be described, along with high-level overviews of the challenges with this approach and the implemented solutions for the solved problems and proposed solutions for the remaining problems.

@@

The solution to this problem is to dynamically move the server-region boundaries to prevent clusters of objects having the majority of the objects outside of their host server region or even avoid be moved to avoid intersecting large clusters of objects entirely. However, this solution is not yet implemented in AP.

@@

1. 3-Object Thrashing - An object may be overlapping two auras from different servers. Given appropriate velocity, this could result in object migration, followed by aura collision, followed by migration and then repeating the process again. For example, Objects K, L and M in Fig. \ref{AuraProj}. Object K lies inside the auras of both Object L and M.

@@

2. 2-Object Thrashing - Two objects on different servers may both trigger the migration of the other. For example, Objects C and D in Fig. \ref{AuraProj}. Suppose the two objects are moving towards each other. Object C collides with the aura of object D and begins migrating to Server 1. Before Object C is received (and the message processed), object D collides with the aura of Object C and begins migrating to Server 0. The two objects remain on different servers and the process can repeat again, indefinitely.

@@

\section{Summary}
In this chapter, the following points have been addressed:
\begin{itemize}
	\item The requirements of a solution to scalable real-time physics.
	\item The challenges of distributing a real-time physics engine and potential solutions.
	\item A description and justification of AP, including the aura calculation.
	\item The implemented solutions to the problems of: 3-object thrashing; islands; and the corner case.
	\item The proposed solutions to: sub-optimal object hosting and 2-object thrashing, which are not yet implemented.
\end{itemize}
